Modeling the impacts of park access on health outcomes: a utility-based accessibility approach

### 2020-09-24 02_parks_data.Rmd

Now we can join the cemeteries data to the parks data and get a single polygons
layer.
```{r write}
open_spaces <- rbind(
  dissolved %>% 
    transmute(id = parknum, name = park_name, acres, courts, playgrounds, trails, 
              type = "park"),
  dissolved_cemeteries %>% 
    transmute(id = source_id, name, acres, courts = FALSE, playgrounds = FALSE, 
              trails = FALSE, type = "cemetery")
  ) %>%
  filter(as.numeric(acres) > 0.5) %>%
  st_simplify(preserveTopology = TRUE)
```

>>>>

Now we can join the cemeteries data to the parks data and get a single polygons
layer.
```{r write}
open_spaces <-  dissolved %>% 
  transmute(id = parknum, name = park_name, acres, courts, playgrounds, trails, 
            type = "park") %>%
  filter(as.numeric(acres) > 0.5) %>%
  st_simplify(preserveTopology = TRUE)
```

### 2020-09-24 04_accessibility.Rmd

compute_logsums <- function(df) {
  df %>%
    left_join(open_spaces %>% st_set_geometry(NULL), by = c("park_id" = "id")) %>%
    # use euc_distance for impossible distances.
    mutate( distance = ifelse(distance < euc_dist, euc_dist, distance) ) %>%
    # convert distances to miles
    mutate_at(c("distance", "euc_dist"), ~ . * 0.000621371) %>%
    # must be at least 1/10 miles
    mutate_at(c("distance", "euc_dist"), ~ ifelse(. < 0.1, 0.1, .)) %>%

@@

```{r nyc10mw}
access_10mw <- st_read("data/nyc_10mw.geojson") %>%
  st_cast("MULTIPOLYGON") %>%
  lwgeom::st_make_valid() %>%
  summarise(d = 1)

>>>>

compute_logsums <- function(df) {
  df %>%
    filter(!is.na(euc_old)) %>%
    left_join(open_spaces %>% st_set_geometry(NULL), by = c("park_id" = "id")) %>%
    # use euc_distance for impossible distances.
    mutate( distance = ifelse(distance < euc_dist, euc_dist, distance) ) %>%
    # convert distances to miles
    mutate_at(c("distance", "euc_dist"), ~ . * 0.000621371) %>%
    # must be at least 1/10 miles
    mutate_at(c("distance", "euc_dist"), ~ ifelse(. < 0.1, 0.1, .)) %>%

@@

```{r nyc10mw}
access_10mw <- st_read("data/nyc_10mw.geojson") %>%
  st_cast("MULTIPOLYGON") %>%
  st_make_valid() %>%
  summarise(d = 1)

### 2020-09-24 05_estimation.Rmd
Write matrix to file
Restore model estimation code
Don't know where this went in the interim, but we're back now.

```{r W}
Wtr <- nb2listw(poly2nb(est_data), style = "W", zero.policy = TRUE)
print(Wtr, zero.policy = TRUE)
```

@@

```{r access_slx}
access_slx <- lmSLX(update(base_formula, physact ~ . + euc_access), 
                   data = est_data, listw = Wtr, zero.policy = TRUE)
access_sdem <- errorsarlm(update(base_formula, physact ~ . + euc_access),
                          data = est_data, listw = Wtr, zero.policy = TRUE, 
                          Durbin = TRUE)
slx_vs_sdem <- list(
  "SDEM" = access_sdem, 
  "SLX" = access_slx
)
```

@@

```{r screen_obesity_models, results="asis"}
view_kable(
  htmlreg(obesity_models, digits = 3, table = FALSE, single.row = TRUE, 
                   caption.above = TRUE, caption = "Spatial Error Model ",
          stars = c(0.001, 0.01, 0.05, 0.1) )
)
```

>>>>

```{r W}
Wtr <- nb2listw(poly2nb(est_data), style = "W", zero.policy = TRUE)
Wtr %>% write_rds("data/Wtr.rds")
print(Wtr, zero.policy = TRUE)
```

@@

```{r access_slx}
access_slx <- lmSLX(update(base_formula, physact ~ . + euc_access), 
                   data = est_data, listw = Wtr, zero.policy = TRUE)
class(access_slx) <- "lm"
access_sdem <- errorsarlm(update(base_formula, physact ~ . + euc_access),
                          data = est_data, listw = Wtr, zero.policy = TRUE, 
                          Durbin = TRUE)
slx_vs_sdem <- list(
  "SDEM" = access_sdem, 
  "SLX" = access_slx
)
```

@@

```{r screen_obesity_models, results="asis"}
view_kable(
  htmlreg(obesity_models, digits = 3, table = FALSE, single.row = TRUE, 
                   caption.above = TRUE, caption = "Spatial Error Model ", ci.force = TRUE,

          stars = c(0.001, 0.01, 0.05, 0.1) )
)
```

### 2020-09-24 manuscript/manuscript.tex

\email{\href{mailto:gregmacfarlane@gmail.com}{\nolinkurl{gregmacfarlane@gmail.com}}}

@@

In a destination choice framework, the tracts represent the ``origins''
and the ``destinations'' are parks and green spaces in New York City. We
retrieved a polygons layer of public parks and greenspaces within New
York City's municipal boundaries and checked it for accuracy and
relevance \citep{nycparks}. Upon inspection, we removed several
facilities that do not qualify as publicly accessible green space, such
as Yankee Stadium, Citi Field, and their surrounding parking lots. We
also removed parks of less than half an acre in size, as these appear to
be predominantly planted medians rather than legitimate public green
space. We consolidated individual geographic polygons comprising a
single facility --- as is the case in Flushing Meadows --- and
eliminated sub-facilities such as tennis courts or baseball fields
included within larger park facilities. Instead of these distinct
sub-facilities, we created variables for each containing park indicating
the presence of sports courts, playgrounds, and trails.

To this dataset of parks and regularized green spaces, we add a polygons
layer of cemeteries in New York that are open to the public. Cemeteries
are important green spaces that can be used for many types of physical
activity. These operations leave us with 1,277 distinct green spaces;
for simplicity we will refer to both parks and cemeteries as ``parks''
going forward. For each park, we calculate the size of the park in
acres.

@@

\caption{\label{tab:tractsdata}Descriptive Statistics of Tract and Park Variables}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{2in}rlrl}
\toprule
  & Description & Minimum & Median (IQR) & Maximum & Source\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Tract Variables, N = 2102}}\\
\hspace{1em}Obesity & Share of adults over 18 who are obese & 9.60 & \makecell{24.50\\ (19.60, 30.50)} & 44.20 & CDC 500 Cities\\
\hspace{1em}Physical Activity & Share of adults over 18 who engage in some leisure-time physical activity & 48.10 & \makecell{69.50\\ (64.70, 74.60)} & 89.10 & CDC 500 Cities\\
\hspace{1em}Income & Median tract income & 9053.00 & \makecell{59,592.50\\ (41,928.25, 79,092.75)} & 250001.00 & ACS\\
\hspace{1em}Density & Households per square kilometer & 9.20 & \makecell{5,848.46\\ (3,173.62, 9,674.36)} & 43621.52 & ACS\\
\hspace{1em}Fulltime & Share of adults over 18 with full-time work & 8.80 & \makecell{49.48\\ (44.45, 55.29)} & 100.00 & ACS\\
\hspace{1em}College & Share of adults over 24 with a college degree & 0.61 & \makecell{16.30\\ (12.37, 20.11)} & 44.94 & ACS\\
\hspace{1em}Single & Share of adults over 18 living alone or in a non-partnership household & 16.38 & \makecell{59.39\\ (50.30, 68.65)} & 100.00 & ACS\\
\hspace{1em}Youth & Share of population under 18 & 0.00 & \makecell{20.54\\ (16.79, 24.92)} & 64.07 & ACS\\
\hspace{1em}Young adults & Share of population between 18 and 34 & 0.00 & \makecell{25.73\\ (21.66, 29.98)} & 86.75 & ACS\\
\hspace{1em}Seniors & Share of population who are 65 and over & 0.00 & \makecell{12.83\\ (9.47, 16.88)} & 89.88 & ACS\\
\hspace{1em}Black & Share of population who is black & 0.00 & \makecell{10.03\\ (2.13, 44.62)} & 220.65 & ACS\\
\hspace{1em}Asian & Share of population who is Asian & 0.00 & \makecell{7.66\\ (2.40, 20.78)} & 88.07 & ACS\\
\hspace{1em}Hispanic & Share of population who is Hispanic & 0.00 & \makecell{19.07\\ (9.39, 41.07)} & 96.27 & ACS\\
\hspace{1em}Other & Share of population who belong to other minority groups & 0.00 & \makecell{0.00\\ (0.00, 0.53)} & 19.47 & ACS\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Park Variables, N = 1277}}\\
\hspace{1em}Size & Park size in acres & 0.50 & \makecell{1.66\\ (0.95, 5.62)} & 1961.00 & NYC\\
\hspace{1em}Courts & Presence of sport courts / ball fields & 0.00 & \makecell{0.00\\ (0.00, 0.00)} & 1.00 & NYC\\
\hspace{1em}Playgrounds & Presence of playgrounds & 0.00 & \makecell{0.00\\ (0.00, 1.00)} & 1.00 & NYC\\
\hspace{1em}Trails & Presence of trails & 0.00 & \makecell{0.00\\ (0.00, 0.00)} & 1.00 & NYC\\
\bottomrule
\end{tabular}}
\end{table*}

@@

To determine which spatial effects specification was appropriate, we
estimated SLX and SDEM models of physical activity participation rates
as a function of tract covariates and accessibility. These two models
are presented in Table \ref{tab:slx-sdem}. With only a few exceptions,
the SLX and SDEM coefficient estimates for corresponding covariates lie
within the 95\% confidence intervals of the other model. A Hausman-style
test \citep{Pace2008} on the coefficients assumes a null hypothesis that
the coefficients are equivalent; this test produces \(p\)-value of only
\(1.307e-23\). Though this statistic is well beneath a common hypothesis
test threshold of \(\alpha = 0.05\), we elect retain the null hypothesis
that the coefficients are equivalent, as the differences are at no point
practically different from each other. The consequences of rejecting the
null hypothesis in this case would be to suggest a model with spatial
dependence of the dependent variable; as stated above, we feel that such
a relationship is unreasonable. As a consequence of these analyses, we
adopt the SDEM specification moving forward as the spatial lag of the
errors is significant and the overal log likelihood of the SDEM is
higher than the SLX specification.

\begin{table*}
\caption{Comparison of SLX and SDEM Coefficients}
\label{tab:slx-sdem}
\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
\toprule
 & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
\cmidrule{2-4}\cmidrule{6-8}
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} & 
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
\midrule
% latex table generated in R 4.0.0 by xtable 1.8-4 package
% Thu Jun  4 16:31:52 2020
 (Intercept) & -15.8424 & -26.8735 & -4.8112 &   & -24.9740 & -41.8930 & -8.0549 \\ 
  log(Density) & 0.0484 & -0.1314 & 0.2282 &   & 0.1775 & 0.0384 & 0.3166 \\ 
  log(Income) & 5.8210 & 5.2977 & 6.3443 &   & 5.9985 & 5.5746 & 6.4224 \\ 
  Fulltime & 0.1150 & 0.0936 & 0.1365 &   & 0.1275 & 0.1090 & 0.1460 \\ 
  College-educated & 0.0012 & -0.0272 & 0.0297 &   & 0.0076 & -0.0158 & 0.0309 \\ 
  Single Adults & -0.0433 & -0.0623 & -0.0244 &   & -0.0362 & -0.0526 & -0.0198 \\ 
  Youth (0-17) & -0.1511 & -0.1830 & -0.1192 &   & -0.1310 & -0.1576 & -0.1045 \\ 
  Young adults (18-34) & 0.0257 & 0.0008 & 0.0505 &   & 0.0295 & 0.0094 & 0.0496 \\ 
  Seniors (65+) & 0.0137 & -0.0185 & 0.0459 &   & 0.0403 & 0.0130 & 0.0677 \\ 
  Black population share & -0.0465 & -0.0584 & -0.0346 &   & -0.0499 & -0.0586 & -0.0411 \\ 
  Asian population share & -0.0686 & -0.0832 & -0.0541 &   & -0.0767 & -0.0873 & -0.0662 \\ 
  Hispanic population share & -0.1017 & -0.1140 & -0.0894 &   & -0.1025 & -0.1116 & -0.0934 \\ 
  Other Minorities & 0.0368 & -0.0643 & 0.1378 &   & 0.0037 & -0.0849 & 0.0923 \\ 
  $\gamma$: log(Density) & 1.2594 & 0.9413 & 1.5774 &   & 1.0985 & 0.7155 & 1.4815 \\ 
  $\gamma$: log(Income) & 2.3930 & 1.5476 & 3.2383 &   & 1.9742 & 0.9465 & 3.0020 \\ 
  $\gamma$: Fulltime & -0.1398 & -0.1804 & -0.0991 &   & -0.0397 & -0.0869 & 0.0076 \\ 
  $\gamma$: College-educated & -0.1312 & -0.1806 & -0.0818 &   & -0.0710 & -0.1305 & -0.0115 \\ 
  $\gamma$: Single Adults & -0.0480 & -0.0821 & -0.0140 &   & -0.0082 & -0.0504 & 0.0339 \\ 
  $\gamma$: Youth (0-17) & -0.1031 & -0.1618 & -0.0445 &   & -0.0108 & -0.0798 & 0.0583 \\ 
  $\gamma$: Young adults (18-34) & 0.1191 & 0.0762 & 0.1619 &   & 0.0842 & 0.0335 & 0.1349 \\ 
  $\gamma$: Seniors (65+) & 0.0108 & -0.0479 & 0.0695 &   & 0.0590 & -0.0102 & 0.1282 \\ 
  $\gamma$: Black population share & 0.0096 & -0.0054 & 0.0247 &   & 0.0010 & -0.0151 & 0.0172 \\ 
  $\gamma$: Asian population share & -0.0661 & -0.0840 & -0.0483 &   & -0.0397 & -0.0583 & -0.0210 \\ 
  $\gamma$: Hispanic population share & -0.0060 & -0.0216 & 0.0097 &   & -0.0010 & -0.0182 & 0.0162 \\ 
  $\gamma$: Other Minorities & 0.1868 & -0.0508 & 0.4244 &   & 0.0726 & -0.1845 & 0.3297 \\ 
  Accessibility & 0.5430 & 0.4195 & 0.6666 &   & 0.1663 & 0.0277 & 0.3048 \\ 
  $\lambda$: spatial correlation &  &  &  &   & 0.6905 & 0.6513 & 0.7296 \\

@@

The coefficients in the SDEM model are of two general types: the direct
effect resulting from a tract's own attributes and the indirect effect
(\(\boldsymbol{\gamma}\)) resulting from the spatially-weighted
attributes of its neighbors. For example, a percentage point increase in
the share of young adults in a tract increases the expected physical
activity rate in a tract by 0.02947 percentage points, and a percentage
point increase in the share of young adults \emph{in neighboring tracts}
increases the expected physical activity rate by an \emph{additional}
0.08417 percentage points. This opportunity to examine spatial
spillovers of attributes is a key benefit of using a spatial model.

@@

\begin{tabular}{l c c c }
\toprule
 & Size and Distance & Amenities & 10-Minute Walk \\
\midrule
Accessibility  & $0.1663^{*}$        & $0.1493^{*}$        & $0.5865$             \\
               & $[0.0277;\ 0.3048]$ & $[0.0073;\ 0.2914]$ & $[-0.1778;\ 1.3508]$ \\
\midrule
Num. obs.      & 2099                & 2099                & 2099                 \\
Parameters     & 28                  & 28                  & 28                   \\
Log Likelihood & -4435.3869          & -4436.0034          & -4436.9264           \\
\bottomrule
\multicolumn{4}{l}{\scriptsize{$^*$ 0 outside the confidence interval 95\% confidence interval in brackets.  $y = $ tract-level physical activity rate.}}
\end{tabular}
\end{table*}

We now consider the impacts of a model where the dependent variable is
the \emph{obesity} rate in a tract, and physical activity becomes an
independent covariate alongside the controlling variables and the
accessibility metrics. Table \ref{tab:obesity-models} presents estimates
of the effect of all three utility-based accessibility measures as well
as the 10-minute walk buffer. As before, the estimates of the other
variables are available in the Appendix. The correlation between
physical activity rates and obesity is clear; for every percentage point
increase in physical activity rate, the expected obesity rate drops by
\(0.43\) percentage points in all four accessiblity specifications. The
indirect effect of physical activity rates on obesity in neighboring
zones is inconsequential, supporting our methodological assertion that
public health variables are not spatially dependent, though the factors
leading to them may be.

@@

\begin{tabular}{l c c c }
\toprule
 & Size and Distance & Amenities & 10-Minute Walk \\
\midrule
Physical Activity           & $-0.4802^{*}$         & $-0.4802^{*}$         & $-0.4803^{*}$         \\
                            & $[-0.5043;\ -0.4561]$ & $[-0.5043;\ -0.4561]$ & $[-0.5044;\ -0.4562]$ \\
$\gamma$: Physical Activity & $0.0197$              & $0.0198$              & $0.0173$              \\
                            & $[-0.0380;\ 0.0775]$  & $[-0.0380;\ 0.0775]$  & $[-0.0404;\ 0.0750]$  \\
Accessibility               & $-0.0403$             & $-0.0429$             & $-0.2630$             \\
                            & $[-0.1158;\ 0.0351]$  & $[-0.1210;\ 0.0352]$  & $[-0.6491;\ 0.1232]$  \\
\midrule
Num. obs.                   & 2099                  & 2099                  & 2099                  \\
Parameters                  & 30                    & 30                    & 30                    \\
Log Likelihood              & -3113.8451            & -3113.8136            & -3113.5028            \\
\bottomrule
\multicolumn{4}{l}{\scriptsize{$^*$ 0 outside the confidence interval 95\% confidence interval in brackets.  $y = $ tract-level obesity rate.}}
\end{tabular}
\end{table*}

>>>>

\email{\href{mailto:gregmacfarlane@byu.edu}{\nolinkurl{gregmacfarlane@byu.edu}}}

@@

In a destination choice framework, the tracts represent the ``origins''
and the ``destinations'' are parks and green spaces in New York City. We
retrieved a polygons layer of public parks and green spaces within New
York City's municipal boundaries and checked it for accuracy and
relevance \citep{nycparks}. Upon inspection, we removed several
facilities that do not qualify as publicly accessible green space, such
as Yankee Stadium, Citi Field, and their surrounding parking lots. We
also removed parks of less than half an acre in size, as these appear to
be predominantly planted medians rather than legitimate public green
space. We consolidated individual geographic polygons comprising a
single facility --- as is the case in Flushing Meadows --- and
eliminated sub-facilities such as tennis courts or baseball fields
included within larger park facilities. Instead of these distinct
sub-facilities, we created variables for each containing park indicating
the presence of sports courts, playgrounds, and trails. These operations
leave us with 1,191 distinct green spaces; For each park, we calculate
the size of the park in acres.

@@

\caption{\label{tab:tractsdata}Descriptive Statistics of Tract and Park Variables}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{2in}rlrl}
\toprule
  & Description & Minimum & Median (IQR) & Maximum & Source\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Tract Variables, N = 2102}}\\
\hspace{1em}Obesity & Share of adults over 18 who are obese & 9.60 & \makecell{24.50\\ (19.60, 30.50)} & 44.20 & CDC 500 Cities\\
\hspace{1em}Physical Activity & Share of adults over 18 who engage in some leisure-time physical activity & 48.10 & \makecell{69.50\\ (64.70, 74.60)} & 89.10 & CDC 500 Cities\\
\hspace{1em}Income & Median tract income & 9053.00 & \makecell{59,592.50\\ (41,928.25, 79,092.75)} & 250001.00 & ACS\\
\hspace{1em}Density & Households per square kilometer & 9.20 & \makecell{5,848.46\\ (3,173.62, 9,674.36)} & 43621.52 & ACS\\
\hspace{1em}Fulltime & Share of adults over 18 with full-time work & 8.80 & \makecell{49.48\\ (44.45, 55.29)} & 100.00 & ACS\\
\hspace{1em}College & Share of adults over 24 with a college degree & 0.61 & \makecell{16.30\\ (12.37, 20.11)} & 44.94 & ACS\\
\hspace{1em}Single & Share of adults over 18 living alone or in a non-partnership household & 16.38 & \makecell{59.39\\ (50.30, 68.65)} & 100.00 & ACS\\
\hspace{1em}Youth & Share of population under 18 & 0.00 & \makecell{20.54\\ (16.79, 24.92)} & 64.07 & ACS\\
\hspace{1em}Young adults & Share of population between 18 and 34 & 0.00 & \makecell{25.73\\ (21.66, 29.98)} & 86.75 & ACS\\
\hspace{1em}Seniors & Share of population who are 65 and over & 0.00 & \makecell{12.83\\ (9.47, 16.88)} & 89.88 & ACS\\
\hspace{1em}Black & Share of population who is black & 0.00 & \makecell{10.03\\ (2.13, 44.62)} & 220.65 & ACS\\
\hspace{1em}Asian & Share of population who is Asian & 0.00 & \makecell{7.66\\ (2.40, 20.78)} & 88.07 & ACS\\
\hspace{1em}Hispanic & Share of population who is Hispanic & 0.00 & \makecell{19.07\\ (9.39, 41.07)} & 96.27 & ACS\\
\hspace{1em}Other & Share of population who belong to other minority groups & 0.00 & \makecell{0.00\\ (0.00, 0.53)} & 19.47 & ACS\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Park Variables, N = 1191}}\\
\hspace{1em}Size & Park size in acres & 0.50 & \makecell{1.57\\ (0.94, 4.45)} & 1961.00 & NYC\\
\hspace{1em}Courts & Presence of sport courts / ball fields & 0.00 & \makecell{0.00\\ (0.00, 0.00)} & 1.00 & NYC\\
\hspace{1em}Playgrounds & Presence of playgrounds & 0.00 & \makecell{0.00\\ (0.00, 1.00)} & 1.00 & NYC\\
\hspace{1em}Trails & Presence of trails & 0.00 & \makecell{0.00\\ (0.00, 0.00)} & 1.00 & NYC\\
\bottomrule
\end{tabular}}
\end{table*}

@@

To determine which spatial effects specification was appropriate, we
estimated SLX and SDEM models of physical activity participation rates
as a function of tract covariates and accessibility. These two models
are presented in Table \ref{tab:slx-sdem}. With only a few exceptions,
the SLX and SDEM coefficient estimates for corresponding covariates lie
within the 95\% confidence intervals of the other model. A Hausman-style
test \citep{Pace2008} on the coefficients assumes a null hypothesis that
the coefficients are equivalent; this test produces \(p\)-value of only
\(1.318e-23\). Though this statistic is well beneath a common hypothesis
test threshold of \(\alpha = 0.05\), we elect retain the null hypothesis
that the coefficients are equivalent, as the differences are at no point
practically different from each other. The consequences of rejecting the
null hypothesis in this case would be to suggest a model with spatial
dependence of the dependent variable; as stated above, we feel that such
a relationship is unreasonable. As a consequence of these analyses, we
adopt the SDEM specification moving forward as the spatial lag of the
errors is significant and the overall log likelihood of the SDEM is
higher than the SLX specification.

\begin{table*}
\caption{Comparison of SLX and SDEM Coefficients}
\label{tab:slx-sdem}
\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
\toprule
 & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
\cmidrule{2-4}\cmidrule{6-8}
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} & 
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
\midrule
% latex table generated in R 4.0.0 by xtable 1.8-4 package
% Tue Sep 22 16:54:49 2020
 (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
  log(Density) & 0.0502 & -0.1280 & 0.2284 &   & 0.1760 & 0.0371 & 0.3150 \\ 
  log(Income) & 5.8667 & 5.3476 & 6.3859 &   & 6.0134 & 5.5901 & 6.4368 \\ 
  Fulltime & 0.1157 & 0.0944 & 0.1369 &   & 0.1271 & 0.1086 & 0.1455 \\ 
  College-educated & 0.0029 & -0.0253 & 0.0311 &   & 0.0077 & -0.0156 & 0.0310 \\ 
  Single Adults & -0.0435 & -0.0623 & -0.0247 &   & -0.0365 & -0.0528 & -0.0201 \\ 
  Youth (0-17) & -0.1528 & -0.1844 & -0.1211 &   & -0.1320 & -0.1585 & -0.1055 \\ 
  Young adults (18-34) & 0.0245 & -0.0001 & 0.0492 &   & 0.0292 & 0.0092 & 0.0493 \\ 
  Seniors (65+) & 0.0108 & -0.0212 & 0.0427 &   & 0.0386 & 0.0112 & 0.0659 \\ 
  Black population share & -0.0471 & -0.0589 & -0.0353 &   & -0.0499 & -0.0586 & -0.0412 \\ 
  Asian population share & -0.0684 & -0.0828 & -0.0540 &   & -0.0764 & -0.0870 & -0.0659 \\ 
  Hispanic population share & -0.1003 & -0.1126 & -0.0881 &   & -0.1023 & -0.1114 & -0.0932 \\ 
  Other Minorities & 0.0341 & -0.0661 & 0.1343 &   & 0.0047 & -0.0837 & 0.0931 \\ 
  $\gamma$: log(Density) & 1.2513 & 0.9367 & 1.5659 &   & 1.0873 & 0.7062 & 1.4684 \\ 
  $\gamma$: log(Income) & 2.3641 & 1.5266 & 3.2016 &   & 1.9780 & 0.9563 & 2.9997 \\ 
  $\gamma$: Fulltime & -0.1346 & -0.1749 & -0.0943 &   & -0.0411 & -0.0882 & 0.0059 \\ 
  $\gamma$: College-educated & -0.1201 & -0.1692 & -0.0711 &   & -0.0704 & -0.1296 & -0.0112 \\ 
  $\gamma$: Single Adults & -0.0520 & -0.0857 & -0.0183 &   & -0.0094 & -0.0514 & 0.0325 \\ 
  $\gamma$: Youth (0-17) & -0.1013 & -0.1594 & -0.0432 &   & -0.0128 & -0.0815 & 0.0559 \\ 
  $\gamma$: Young adults (18-34) & 0.1131 & 0.0706 & 0.1555 &   & 0.0838 & 0.0334 & 0.1342 \\ 
  $\gamma$: Seniors (65+) & 0.0015 & -0.0568 & 0.0598 &   & 0.0545 & -0.0145 & 0.1235 \\ 
  $\gamma$: Black population share & 0.0099 & -0.0051 & 0.0248 &   & 0.0011 & -0.0149 & 0.0172 \\ 
  $\gamma$: Asian population share & -0.0644 & -0.0821 & -0.0467 &   & -0.0397 & -0.0582 & -0.0212 \\ 
  $\gamma$: Hispanic population share & -0.0074 & -0.0229 & 0.0081 &   & -0.0015 & -0.0185 & 0.0156 \\ 
  $\gamma$: Other Minorities & 0.1629 & -0.0725 & 0.3983 &   & 0.0723 & -0.1840 & 0.3286 \\ 
  Accessibility & 0.6575 & 0.5348 & 0.7801 &   & 0.2306 & 0.0907 & 0.3705 \\ 
  $\lambda$: spatial correlation &  &  &  &   & 0.6854 & 0.6459 & 0.7249 \\

@@

The coefficients in the SDEM model are of two general types: the direct
effect resulting from a tract's own attributes and the indirect effect
(\(\boldsymbol{\gamma}\)) resulting from the spatially-weighted
attributes of its neighbors. For example, a percentage point increase in
the share of young adults in a tract increases the expected physical
activity rate in a tract by 0.02922 percentage points, and a percentage
point increase in the share of young adults \emph{in neighboring tracts}
increases the expected physical activity rate by an \emph{additional}
0.08378 percentage points. This opportunity to examine spatial
spillovers of attributes is a key benefit of using a spatial model.

@@

\begin{tabular}{l c c c}
\toprule
 & Size and Distance & Amenities & 10-Minute Walk \\
\midrule
Accessibility  & $0.2306^{*}$        & $0.1923^{*}$        & $0.5865$             \\
               & $ [0.0907; 0.3705]$ & $ [0.0498; 0.3347]$ & $ [-0.1778; 1.3508]$ \\
\midrule
Num. obs.      & $2099$              & $2099$              & $2099$               \\
Parameters     & $28$                & $28$                & $28$                 \\
Log Likelihood & $-4433.0965$        & $-4434.7087$        & $-4436.9264$         \\
\bottomrule
\multicolumn{4}{l}{\scriptsize{$^*$ Null hypothesis value outside the confidence interval. 95\% confidence interval in brackets.  $y = $ tract-level physical activity rate.}}
\end{tabular}
\end{table*}

We now consider the impacts of a model where the dependent variable is
the \emph{obesity} rate in a tract, and physical activity becomes an
independent covariate alongside the controlling variables and the
accessibility metrics. Table \ref{tab:obesity-models} presents estimates
of the effect of all three utility-based accessibility measures as well
as the 10-minute walk buffer. As before, the estimates of the other
variables are available in Table \ref{tab:ob-fullmodels} of the
Supplementary Material. The correlation between physical activity rates
and obesity is clear; for every percentage point increase in physical
activity rate, the expected obesity rate drops by \(0.43\) percentage
points in all four accessibility specifications. The indirect effect of
physical activity rates on obesity in neighboring zones is
inconsequential, supporting our methodological assertion that public
health variables are not spatially dependent, though the factors leading
to them may be.

@@

\begin{tabular}{l c c c}
\toprule
 & Size and Distance & Amenities & 10-Minute Walk \\
\midrule
Physical Activity           & $-0.4798^{*}$         & $-0.4800^{*}$         & $-0.4803^{*}$         \\
                            & $ [-0.5039; -0.4556]$ & $ [-0.5041; -0.4558]$ & $ [-0.5044; -0.4562]$ \\
$\gamma$: Physical Activity & $0.0207$              & $0.0204$              & $0.0173$              \\
                            & $ [-0.0371;  0.0785]$ & $ [-0.0375;  0.0782]$ & $ [-0.0404;  0.0750]$ \\
Accessibility               & $-0.0495$             & $-0.0471$             & $-0.2630$             \\
                            & $ [-0.1260;  0.0270]$ & $ [-0.1259;  0.0316]$ & $ [-0.6491;  0.1232]$ \\
\midrule
Num. obs.                   & $2099$                & $2099$                & $2099$                \\
Parameters                  & $30$                  & $30$                  & $30$                  \\
Log Likelihood              & $-3113.5891$          & $-3113.7048$          & $-3113.5028$          \\
\bottomrule
\multicolumn{4}{l}{\scriptsize{$^*$ Null hypothesis value outside the confidence interval. 95\% confidence interval in brackets.  $y = $ tract-level obesity rate.}}
\end{tabular}
\end{table*}
